\ttlfnt{Comparing the performance of websites and their content distribution networks}

### 2016-08-26 Writeup/paper.tex
Add a 'Measurement Location' subsection to Method

\begin{itemize}
	\item Different ISPs? \\
	\item All the same location - CONSISTENCY
\end{itemize}

>>>>

\subsection{Measurement Location}
We measure two different scenarios: Home networks and Institutional networks. In the case of home networks, all our measurements were done from the same location (in order to ensure consistency in our results). Home network measurements were taken while connected to five different ISPs (namely Afrihost, Axxess, Cybersmart, Telkom, and WebAfrica) for comparison.

In the case of institutional networks, all our measurements were done while connected to the UCT network. This test was added in order to compare the results from a home network to what one might get on a network with significantly higher bandwidth.
